---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# resourcecodedata

This a data-only R package. It contains the **Resourcecode** hindcast database configuration data, that is used to run the WWIIIⓇ model:
nodes locations for both the sea-state parameters, examples of time series of 1D and 2D surface elevation variance spectral density, etc. These are static data that will **never** be updated.

For more on using these data, see the GitHub repository for the [resourcecode](https://github.com/Resourcecode-project/r-resourcecode) package, which is built to interact with data in this package.

## Installation

You can install the development version of `{resourcecodedata}` like so, thanks to the `{drat}` package:

```{r}
install.packages("resourcecodedata",type = "source",repos = "resourcecode-project.github.io/drat")
```

or from install from
[r-universe](https://resourcecode-project.r-universe.dev/resourcecodedata):

```{r}
install.packages("resourcecodedata", repos = c("https://resourcecode-project.r-universe.dev", "https://cloud.r-project.org"))
```

